A comprehensive framework to capture the arcana of neuroimaging analysis

### 2018-10-15 manuscript/manuscript.tex
touched up manuscript and examples

Pipelines are included in the analysis suite of a Study class by
defining a method in the class that constructs and returns a
\emph{Pipeline} object, and referencing that method in the class' data
specification table. Pipeline objects are thin wrappers around Nipype
workflows, which manage the namespaces of the workflow nodes, and should
be created in constructor methods using the \emph{Study.new\_pipeline}
method (Figure \ref{fig:pipeline_constructor}).

@@

At instantiation (via the new\_pipeline method) a Pipeline is passed the
following arguments:

\begin{itemize}
\item
  \begin{quote}
  A name for the pipeline
  \end{quote}
\item
  \begin{quote}
  The inputs to the pipeline
  \end{quote}
\item
  \begin{quote}
  The output specifications the pipeline
  \end{quote}
\item
  \begin{quote}
  Description of the pipeline
  \end{quote}
\item
  \begin{quote}
  A list of scientific references the analysis was informed by
  \end{quote}
\item
  \begin{quote}
  Keyword arguments passed directly from the pipeline constructor method
  \end{quote}
\end{itemize}

Inputs and outputs refer to entries in the data specification table and
specify the file formats (fileset) or data type (field) that the input
is expected in, or the output will be returned in. If this
format/data-type differs from that specified in the data specification
table then an implicit conversion will be performed when the pipeline is
executed, thereby making data conversion transparent to the researcher.
Every pipeline constructor should take only wildcard keyword arguments
(i.e. **kwargs), which should be passed directly through to the
new\_pipeline method to enable modification of the pipeline namespace by
overriding methods in subclasses.

@@

@@

\begin{table}
\caption{Storage locations of derived data for each repository
type. Derivatives are stored in separate namespaces for each Study
instance to enable multiple analyses on the same datasets with different
parameterisations. Where `...' is the location of the
directory or MrSession that holds the derivatives, \emph{subj} = subject ID, \emph{vis} = visit ID,
\emph{study} = name of the Study instance, and \emph{pl} = name
of pipeline.}
\label{tbl:repo-structure} 
\begin{tabular}{llll}
\hline\noalign{\smallskip}
\textbf{Type} & \textbf{Plain-directory} & \textbf{BIDS} & \textbf{XNAT}  \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\textbf{Derivatives} & /\emph{subj}/\emph{vis}/\emph{study} & /derivatives/\emph{study}/\emph{subj}/\emph{vis} & /\emph{subj}/\emph{vis}\_\emph{study}\\
\textbf{Fields} & \D/\_\_fields\_\_.json & \D/\_\_fields\_\_.json & MrSession XML \\ 
\textbf{Provenance} & \D/\_\_prov\_\_/\emph{pl}.json & \D/\_\_prov\_\_/\emph{pl}.json & \D/\_\_prov\_\_/\emph{pl}.json \\
\noalign{\smallskip}\hline
\end{tabular}
\end{table}

@@

\begin{table}
\caption{Abstract methods in the base Repository class that
need to be implemented by platform-specific sub-classes.}
\label{tbl:abstract-repo-methods} 
\begin{tabular}{ll}
\hline\noalign{\smallskip}
\textbf{Method name} & \textbf{Function} \\
\noalign{\smallskip}\hline\noalign{\smallskip}
find\_data() & Queries repository to find all existing filesets and
fields \\
get\_fileset(Fileset) & Caches file-set (if necessary) and returns the file path. \\
get\_field(Field) & Retrieves and returns the value of the field from
the repository \\
put\_fileset(Fileset) & Inserts file-set into the repository and updates cache. \\
put\_field(Field) & Inserts the value of the Field into the repository \\
connect() & Opens a connection to the repository (optional). \\
disconnect() & Closes connection to repository (optional)\\
\noalign{\smallskip}\hline
\end{tabular}
\end{table}

>>>>

Pipelines are included in the analysis suite of a Study class by
defining a method in the class that constructs and returns a
\emph{Pipeline} object, and referencing the method by name in a FilesetSpec
or FieldSpec in the class' data specification table. Pipeline objects are thin
wrappers around Nipype workflows, which manage the namespaces of the
workflow nodes, and should be created in constructor methods using the
\emph{pipeline} method of the Study class (Figure \ref{fig:pipeline_constructor}).

@@

% Need to introduce and explain new syntax

@@

At initialisation, a Pipeline is given a name, which must be unique amongst the
pipelines that can be constructed by the Study. A description of the pipeline and
the list of scientific references

Study class Inputs and outputs refer to entries in the data specification table and
specify the file formats (fileset) or data type (field) that the input
is expected in, or the output will be returned in. If this
format/data-type differs from that specified in the data specification
table then an implicit conversion will be performed when the pipeline is
executed, thereby making data conversion transparent to the researcher.
Every pipeline constructor should take only wildcard keyword arguments
(i.e. **kwargs), which should be passed directly through to the
new\_pipeline method to enable modification of the pipeline namespace by
overriding methods in subclasses.

% End reworked syntax explanation

@@

\begin{table}
\caption{Storage locations of derived data for each repository
type. Derivatives are stored in separate namespaces for each Study
instance to enable multiple analyses on the same datasets with different
parameterisations. Where `...' is the location of the
directory or MrSession that holds the derivatives, \emph{subj} = subject ID, \emph{vis} = visit ID,
\emph{study} = name of the Study instance, and \emph{pl} = name
of pipeline.}
\label{tbl:repo-structure} 
\begin{tabular}{llll}
\hline\noalign{\smallskip}
\textbf{Datatype} & \textbf{Plain-directory} & \textbf{BIDS} & \textbf{XNAT}  \\
\noalign{\smallskip}\hline\noalign{\smallskip}
Derivatives & /\emph{subj}/\emph{vis}/\emph{study} & /derivatives/\emph{study}/\emph{subj}/\emph{vis} & /\emph{subj}/\emph{vis}\_\emph{study}\\
Fields & \D/\_\_fields\_\_.json & \D/\_\_fields\_\_.json & MrSession XML \\ 
Provenance & \D/\_\_prov\_\_/\emph{pl}.json & \D/\_\_prov\_\_/\emph{pl}.json & \D/\_\_prov\_\_/\emph{pl}.json \\
\noalign{\smallskip}\hline
\end{tabular}
\end{table}

@@

\begin{table}
\caption{Abstract methods in the base Repository class that
need to be implemented by platform-specific sub-classes.}
\label{tbl:abstract-repo-methods} 
\begin{tabular}{ll}
\hline\noalign{\smallskip}
\textbf{Method name} & \textbf{Function} \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\emph{find\_data()} & Queries repository to find all existing filesets and
fields \\
\emph{get\_fileset(Fileset)} & Caches file-set (if necessary) and returns the file path. \\
\emph{get\_field(Field)} & Retrieves and returns the value of the field from
the repository \\
\emph{put\_fileset(Fileset)} & Inserts file-set into the repository and updates cache. \\
\emph{put\_field(Field)} & Inserts the value of the Field into the repository \\
\emph{connect()} & Opens a connection to the repository (optional). \\
\emph{disconnect()} & Closes connection to repository (optional)\\
\noalign{\smallskip}\hline
\end{tabular}
\end{table}
